BioTime

### 2020-09-04 data-raw/biotime.Rmd
Label all plots not just NA's

#replace plot NA's that are really studies with only one plot with a plot label 
data <- data %>% 
  mutate(plot = case_when(
    study_id %in% sing_study & is.na(plot) ~ "A",
    TRUE ~ plot
  ))
```

>>>>

#replace plot NA's that are really studies with only one plot with a plot label 
data <- data %>% 
  mutate(plot = case_when(
    study_id %in% sing_study & plot %in% c(NA, "", "#REF!") ~ "A",
    TRUE ~ plot
  ))
```
